\subsection{{Senior Advisor~~|~~Advanced Analytics \& Data Sciences~~|~~Manufacturing \& Supply Chain \hfill 2022-Present}}
\subtext{Eli Lilly \& Company \hfill Indianapolis, IN}
\begin{zitemize}
\item Developed agentic AI prototype using AutoGen and OptiGuide that autonomously modifies Pyomo optimization model constraints and structure, reducing scenario evaluation from hours to minutes and eliminating manual model reconfiguration (demonstrated via Streamlit interface).
\item Built risk-aware transformer forecasting models (T5 with LoRA fine-tuning) for tirzepatide sales, penalizing underprediction to reduce stockout risk, integrated into production ensemble framework for inventory recommendations across market-SKU combinations.
\item Built end-to-end supply chain optimization platform for worldwide distribution of 500M+ devices using Python/Pyomo with Streamlit frontend on Kubernetes, supporting monthly S\&OP cycles for global orchestration teams.
\item Increased manufacturing capacity by 5M devices annually through ML-driven production line optimization, including dynamic time warping for root-cause downtime analysis {\color{customcolor} (patent pending)} and Bayesian anomaly detection {\color{customcolor} (patent pending)}.
\item Designed physics-informed simulation framework combining ODEs with real fault data to optimize conveyor layouts {\color{customcolor} (patent pending)}, driving \$2M+ infrastructure investments that unlocked 1.5M additional devices annually.
\item Developed neural ODE models for pharmacodynamic forecasting with asymmetric loss functions penalizing glucose overprediction, reducing hypoglycemia risk in insulin dosing control while maintaining prediction accuracy.
\item Scaled team effectiveness by mentoring 2 PhD interns, creating technical onboarding framework (Git workflows, documentation standards), and accelerating 4 new hire integrations.
\end{zitemize}

%====================
% EXPERIENCE A
%====================
\subsection{{Machine Learning Researcher~~|~~Optimization \& Time-Series Forecasting in Chaotic Systems \hfill 2019-2022}}
\subtext{Johns Hopkins University \hfill Baltimore, MD}
\begin{zitemize}
\item Reduced computational cost by 50\%+ through novel sensor-weighting algorithm that optimizes Hessian curvature, enabling faster convergence in high-dimensional optimization problems.
\item Developed custom backpropagation framework for exact gradient computation in time-series forecasting models.
\item Secured \$450K in research funding by translating complex ML/optimization concepts into compelling technical demonstrations.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Research Scientist~~|~~Predictive Modeling \& ML for Complex Systems \hfill 2016-2019}}
\subtext{University of Illinois at Urbana--Champaign \hfill Champaign, IL}
\begin{zitemize}
\item Developed ignition prediction models with quantified uncertainty for \$20M DOE-funded research center.
\item Built CNN-based ML pipeline to accelerate combustion predictions, reducing simulation time while maintaining accuracy.
\item Led cross-functional team coordination and sprint planning to meet aggressive delivery deadlines.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Graduate Researcher~~|~~Time-Series Analysis \& Statistical Modeling \hfill 2012-2016}}
\subtext{University of Illinois at Urbana--Champaign \hfill Champaign, IL}
\begin{zitemize}
\item Developed novel statistical models for anomaly detection in chaotic time-series data using higher-order statistics and spectral analysis.
\item Built and managed 50TB+ simulation database pipeline in Fortran, processing large-scale datasets for pattern recognition and feature extraction.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Software Engineer / Researcher~~|~~Monte Carlo Simulation \& Risk Modeling \hfill 2010-2012}}
\subtext{Battelle Memorial Institute \hfill Columbus, OH}
\begin{zitemize}
\item Built high-performance Monte Carlo simulation engine in object-oriented C++ for supply chain risk assessment, delivering mission-critical analytics to DHS under tight deadlines.
\item Designed custom probability distribution libraries and data ingestion pipelines for expert survey data.
\item Implemented comprehensive testing framework including unit, integration, and validation tests ensuring model correctness and reliability.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}